Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-04-08 man/ms.Rmd
add drought event as method and remove from table

@@

The values of these indices were computed for tree growth (BAI) and greenness (EVI mean) during each drought event. 2005 and 2012 were considered as single drought events. The predrought and postdrought values of each target variable (*i.e.*: BAI or EVI) were computed as the mean value during a period of three years before and after the drought event respectively. A period of three years was chosen because we found similar results comparing periods of two, three and four years (Figure S6) and this length was used in other studies [*e.g.* @Gazol2017]. To put in context in a longer-term the resilience observed for 2005 and 2012 drought events, as well as to test whether the resilience indices were ecologically meaningful, resilience metrics for BAI data were additionally computed for the most severe drought events since 1900 and compared them with drought severity (Figure S5).

>>>>

To identify drought events at long-term perspective we used SPEI index (12 months) for all 0.5º grid cells covering Sierra Nevada obtainde from Global SPEI Database (http://spei.csic.es/database.html). A drought event starts in the month when SPEI falls below the threshold of -1.28 [@Pascoa2017]. A drought event is considered only when SPEI values are below the threshold for at least two consecutive months [*e.g.* @Spinoni2015; @Spinoni2017a; @Pascoa2017]. Several indicators were computed for each drought event: ***duration*** as the number of consecutive months with the SPEI lower than a certain threshold; ***severity*** of a drought event is the sum of the SPEI values (absolute values) during the duration of the drought event; the ***intensity*** and the ***Lowest SPEI*** refer to the mean and lowest value of SPEI respectively during the drought event duration.

@@

The values of these indices were computed for tree growth (BAI) and greenness (EVI mean) during each drought event. 2005 and 2012 were considered as single drought events. The predrought and postdrought values of each target variable (*i.e.*: BAI or EVI) were computed as the mean value during a period of three years before and after the drought event respectively. A period of three years was chosen because we found similar results comparing periods of two, three and four years (Figure S6) and this length was used in other studies [*e.g.* @Gazol2017]. To put in context in a longer-term the resilience observed for 2005 and 2012 drought events, as well as to test whether the resilience indices were ecologically meaningful, resilience metrics for BAI data were additionally computed for the most severe drought events since 1900 and compared them with drought severity (Figure 6, Table S3).

### 2019-04-08 man/tables/t_droughts.Rmd
add drought event as method and remove from table

##### 
**Table S3.** Drought events for Sierra Nevada based on SPEI index (12 months scale). A drought event starts in the month when SPEI falls below the threshold of -1.28 [@Pascoa2017]. A drought event is considered only when SPEI values are below the threshold for at least two consecutive months [*e.g.* @Spinoni2015; @Spinoni2017a; @Pascoa2017]. The ***duration*** of a drought event is the number of consecutive months with the SPEI lower than a certain threshold. ***Severity*** of a drought event is the sum of the SPEI values (absolute values) during the duration of the drought event. ***Intensity*** and ***Lowest SPEI*** refer to the mean and lowest value of SPEI respectively during the drought event duration. SPEI data were obtained for all 0.5º grid cells covering Sierra Nevada.

>>>>

##### 
**Table S3.** Drought events for Sierra Nevada based on SPEI index (12 months scale). See methods for details.
